---
title: "Data Import"
---

This Skript imports both the stock data from crisp as well as the index data from crisp.
Aditionally, the data is reshaped and cleaned.
Lastly, the datasets are saved.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readr)
library(tidyr)
library(reshape2)
library(xts)
library(stringi)
```

```{r}
rm(list=ls())
```


Import data

```{r, echo=FALSE, warning=FALSE}

data.stock <- read_csv("../../Data/Stock_data_2017_12.csv",col_types = cols(date = col_date(format = "%d/%m/%Y")))
data.index <- read_csv("../../Data/Index_data_2017_12.csv", col_types = cols(caldt = col_date(format = "%d/%m/%Y")))
```


# Creating Adjusted Price, Shares Outstanding and Market Cap

Adjusting Price
```{r}
data.stock$"ADJUSTED CLOSING PRICE" <- data.stock$PRC / data.stock$CFACPR
```

Adjusting Shares outstanding
```{r}
data.stock$"ADJUSTED SHARES OUTSTANDING" <- data.stock$SHROUT / data.stock$CFACSHR * 1000
```

Market Cap
```{r}
data.stock$"MARKET CAP" <- data.stock$`ADJUSTED CLOSING PRICE` * data.stock$`ADJUSTED SHARES OUTSTANDING`
```


# Cleaning Data

```{r}
# Deleting all rows with missing prices
data.stock <- data.stock[!is.na(data.stock$`ADJUSTED CLOSING PRICE`),]

# Deleting 1989
data.stock <- data.stock[!(data.stock$date=="1989-12-29"),]


# Deleting double instances 
data.stock <- data.stock[!(data.stock$PERMNO==75519),]
data.stock <- data.stock[!(data.stock$PERMNO==75044),]

# Changing PERCO of Wells Fargo because it was aquired in 89
data.stock <- data.stock[!(data.stock$PERMCO==21902),]
```

```{r}
stock.number <- length(unique(data.stock$PERMCO))
```


Create Index

```{r}
data.index <- data.index[c("caldt","spindx","sprtrn","usdval")]
colnames(data.index) <- c("date","Price","Return","Market Cap")
```

# Price

Reorder data and creat subset for reformatting from long to wide

```{r}
dailyprice <- data.stock[c("date","PERMCO","ADJUSTED CLOSING PRICE")]
```

Long to wide
```{r}
dailyprice <- dcast(dailyprice, date ~ PERMCO,fun.aggregate = NULL,value.var = "ADJUSTED CLOSING PRICE")

dailyprice[-1] <- abs(dailyprice[-1])

dailyprice[,length(dailyprice)+1] <- data.index[2]

date <- as.Date(dailyprice[,1],"%d/%m/%Y")
dailyprice <- as.xts(dailyprice[-1],order.by=date)
```



# Return

Reorder data and creat subset for reformatting from long to wide

```{r}
dailyreturn <- data.stock[c("date","PERMCO","RET")]
```

Long to wide
```{r}
dailyreturn <- dcast(dailyreturn, date ~ PERMCO,fun.aggregate = NULL,value.var = "RET")
dailyreturn[,length(dailyreturn)+1] <- data.index[3]
dailyreturn <- as.xts(dailyreturn[-1],order.by=date)

```

Simple to log return

```{r}
dailyreturn[] <- log(dailyreturn[]+1)
```

# Market Cap

```{r}
dailymarketcap <- data.stock[c("date","PERMCO","MARKET CAP")]
```

Long to wide

```{r}
dailymarketcap <- dcast(dailymarketcap, date ~ PERMCO,fun.aggregate = NULL,value.var = "MARKET CAP")

dailymarketcap[-1] <- abs(dailymarketcap[-1])

dailymarketcap[,length(dailymarketcap)+1] <- data.index[4]*1000

date <- as.Date(dailymarketcap[,1],"%d/%m/%Y")
dailymarketcap <- as.xts(dailymarketcap[-1],order.by=date)
```

Find company names

```{r}
stock.name <- as.vector(t(data.stock[data.stock$date=="2017-12-29",][4]))

# Muss h??ndisch angepasst werden!
stock.name[23] <- "MORGAN STANLEY GROUP INC" # Abfuck in der Datenbank

stock.name[length(stock.name)+1] <- "S&P 500" # Index

stock.name <- stri_trans_totitle(stock.name)

colnames(dailyprice) <- stock.name
colnames(dailyreturn) <- stock.name
colnames(dailymarketcap) <- stock.name

stock.number <- length(stock.name)
```

# Clean Data

Drop some companies

```{r}
stock.drop <- c("C N O Financial Group Inc","C I T Group Inc New","Ally Financial Inc","Voya Financial Inc","Brighthouse Financial Inc")

stock.name <- names(dailyreturn)[!names(dailyreturn) %in% stock.drop]

dailyprice <- dailyprice[,stock.name]
dailyreturn <- dailyreturn[,stock.name]
dailymarketcap <- dailymarketcap[,stock.name]
```

Dropped for the following reason

C N O Financial Group Inc - Bancrupt druing 2003/4
C I T Group Inc New - Bancrupt druing 20010
Ally Financial Inc- Data start 2014
Voya Financial Inc - Data start 2014
Brighthouse Financial Inc - Data start 2017


Clean data

```{r}
# Fill in 1 missing value in BOK
dailyreturn["1991-12-17","B O K Financial Corp" ] <- 0

dailyreturn["2001-09-17/2001-10-05","B G C Partners Inc"] <- 0
```

weekly returns

```{r}
weeklyreturn <- apply.weekly(dailyreturn,colSums)
monthlyreturn <- apply.monthly(dailyreturn,colSums)
```

Sort data

```{r}
dailyprice <- dailyprice[,order(names(dailyprice))]
dailyreturn <- dailyreturn[,order(names(dailyreturn))]
weeklyreturn <- weeklyreturn[,order(names(weeklyreturn))]
dailymarketcap <- dailymarketcap[,order(names(dailymarketcap))]
```


# Number of Obs

```{r}
observations <- data.frame(matrix(nrow=7,ncol=1),row.names = c("Daily","Weekly","Monthly","2000-","2004-","2010-","2015-"))

observations[1,1] <- length(dailyreturn)
observations[2,1] <- length(weeklyreturn)
observations[3,1] <- length(monthlyreturn)
observations[4,1] <- length(dailyreturn["2000/"])
observations[5,1] <- length(dailyreturn["2004/"])
observations[6,1] <- length(dailyreturn["2010/"])
observations[7,1] <- length(dailyreturn["2015/"])

```

```{r}
colnames(dailyreturn)
```

```{r}
dailyreturn <- dailyreturn
colnames(dailyreturn)[19] <- "J.P. Morgan Chase & Co"
colnames(dailyreturn)[5] <- "BGC Partners Inc"
colnames(dailyreturn)[6] <- "BOK Financial Corp"
colnames(dailyreturn)[13] <- "Fulton Financial Corp" 
colnames(dailyreturn)[21] <- "MBIA Inc" 
colnames(dailyreturn)[27] <- "S V B Financial Group" 
colnames(dailyreturn)[29] <- "UMB Financial Corp"
colnames(dailyreturn)

```

Save data

```{r}
#save(dailyprice,file="../R data/dailyprice.Rda")
save(dailyreturn,file="../R data/dailyreturn.Rda")
#save(weeklyreturn,file="../R data/weeklyreturn.Rda")
#save(dailymarketcap,file="../R data/dailymarketcap.Rda")
```
