---
title: "Regression"
---

```{r}
rm(list =ls())
```

```{r}
library(xtable)
library(ggplot2)
```


```{r}
load("~/Dropbox/Research Seminar/R/R data/result_01.Rda")
mydata <- result_01_reg
```


# Regression SRISK SSVAR

```{r}
reg_data <- result_01[-9,c(3,15)]
xtable(summary(lm(reg_data$`SRISK in Mrd. $`~reg_data$`CoVar in Mrd. $`)))
```

```{r}
SSVAR_percent <- CoVaR_Mrd_USD/Marketcap_Mrd_USD
```

# Plot

```{r}
plot(SRISK_Mrd_USD,SSVAR_percent)
summary(lm(SRISK_Mrd_USD ~ SSVAR_percent + Marketcap_Mrd_USD))
```


# Correlation


```{r}
regression3 <- lm(SRISK_Mrd_USD ~ CoVaR_Mrd_USD, mydata)
summary(regression3)

corr_nor <- cor.test(x=CoVaR_Mrd_USD, y=SRISK_Mrd_USD, method = 'pearson')

corr_rank <- cor.test(x=CoVaR_Mrd_USD, y=SRISK_Mrd_USD, method = 'spearman')

corr_rank <- cor.test(x=SRISK_Mrd_USD, y=SSVAR_percent, method = 'spearman')

corr_nor
corr_rank
```






**Data Anaylysis**

*Outline*

1. What are the factors that influence SRISK?

- Higher Cor -> hiher SRISK
- Higher Marketcap higher SRISK

2. What are the factors that influence VaR 1% ? 

2. What are the factors that influence VaR 50% ?

3. What are the factors that influence VaR Sensibility?

4. What are the factors that influence CoVaR?

5. What is the connection between CoVaR and SRISK?



```{r}
regression1 <- lm(SRISK_Mrd_USD ~ Marketcap_Mrd_USD, mydata)
summary(regression1)
```

```{r}
regression2 <- lm(SRISK_Mrd_USD ~ VaR_Diff_Mrd_USD, mydata)
summary(regression2)
```




```{r}
regression1 <- lm(SRISK_Mrd_USD ~  LRMES + Beta + Cor + Vol + Lvg+ Marketcap_Mrd_USD, mydata)
summary(regression1)
```

```{r}
regression1 <- lm(SRISK_Mrd_USD ~ CoVaR_Mrd_USD + Coefficient_01, mydata)
summary(regression1)
```


```{r}
test <- mydata[order(mydata$Industry,-mydata$Marketcap_Mrd_USD),c(2,9)]

```



```{r,message=FALSE}
attach(result_01_reg)
names <- row.names(mydata)

setwd("~/Dropbox/Research Seminar/R/Graphs/Ergebnisse")
png("Scatter_SRISK_CoVaR_01.png",width = 1400, height = 1000, res=110)

plot(CoVaR_Mrd_USD,SRISK_Mrd_USD,ylab="SRISK in Mrd.",xlab="CoVar in Mrd.",ylim=c(-45,0),xlim=c(-45,0))
text(CoVaR_Mrd_USD, SRISK_Mrd_USD,labels=names, cex=1 ,pos=4, offset = 0.7)
#abline(lm(SRISK_Mrd_USD[CoVaR_Mrd_USD>-4] ~ CoVaR_Mrd_USD[CoVaR_Mrd_USD>-4]),lty=2)
abline(lm(SRISK_Mrd_USD ~ CoVaR_Mrd_USD),lty=1)
title("Scatterplot of SRISK and CoVaR (1% VaR and VaR sensibility")
legend(-20, -40, legend=c("Complete sample", "Without outliers (CoVar < -4"), lty=1:2, cex=0.8)

dev.off()

```

```{r}
names(mydata)
```

Is there a connection between VaR Diff and VaR sensibility?
===========================================================

A:
Yes there is a very clear connection. A linear regression and the scatterplot shows that institutions with a higher VaR Diff in % tend to have a higher VaR Sensibility.


```{r,message=FALSE}
i <- 5

attach(mydata)
names <- row.names(mydata[VaR_Diff<(-i),])

plot(VaR_Diff,Coefficient_01,ylab="VaR Sensibility",xlab="VaR Diff. in %") #,ylim=c(-45,0),xlim=c(-8,0))
text(VaR_Diff[VaR_Diff<(-i)],Coefficient_01[VaR_Diff<(-i)],labels=names, cex=0.75 ,pos=4, offset = 0.7)
#abline(lm(SRISK_Mrd_USD[CoVaR_Mrd_USD>-4] ~ CoVaR_Mrd_USD[CoVaR_Mrd_USD>-4]),lty=2)
abline(lm(Coefficient_01 ~ VaR_Diff),lty=1)
title("Scatterplot of VaR Diff and VaR Sens")
legend(-8, -40, legend=c("Complete sample", "Without outliers (CoVar < -4"),
       , lty=1:2, cex=0.8)

reg1 <- summary(lm(Coefficient_01 ~ VaR_Diff))
plot(residuals(reg1))

summary(lm(SRISK_Mrd_USD ~ VaR_Diff_Mrd_USD))
```


```{r}
plot(x,y,
     ylab="SRISK in Mrd. $",xlab="CoVaR in Mrd. $",
     xlim = c(-45,0),ylim = c(-45,0),las=1)

text(text.x,text.y,labels=text.lab, cex=0.7 ,pos=pos, offset = 0.7)
abline(a=0,b=1,lty=2)
abline(lm(y ~ x),lty=1)
```



```{r}
attach(mydata)
names <- row.names(mydata)

plot(Coefficient_01,SRISK_Mrd_USD,ylab="SRISK in Mrd.",xlab="1% Qreg coefficient",ylim=c(-40,0))
#text(Coefficient_01, SRISK_Mrd_USD,labels=names, cex=1 ,pos=4, offset = 0.7)
```

FRAGE:
Was erkl??rt den coefficient?
============================

The regression shows that the coefficient is at least partly correlated to the Beta and the leverage of the institutaions.
Additionally, it is also correlated to the 5% VaR quantile. ????

```{r}
regression1 <- lm(Coefficient_01  ~  VaR_quantil_01 + Beta + Lvg, mydata)
summary(regression1)
```

FRAGE:
Which variables influence the 5% VaR quantile?
============================

Financial Institutions with a higher beta and a higher leverage tend to have higher 5% VaR quntiles. Both Coefficients are significant on the 1% level.

```{r}
regression1 <- lm(VaR_quantil_01  ~  Beta  + LRMES + Cor + Vol, mydata)
summary(regression1)
```




