---
title: "Regression"
---

```{r}
rm(list =ls())
```

```{r}
load("~/Dropbox/Research Seminar/R/R data/result_05.Rda")
```

```{r}
regression1 <- lm(SRISK_Mrd_USD ~ Marketcap_Mrd_USD, result_05_reg)
summary(regression1)
```

```{r}
result_05_reg
regression1 <- lm(SRISK_Mrd_USD ~ VaR_Diff_Mrd_USD , result_05_reg)
summary(regression1)
```


```{r}
regression1 <- lm(SRISK_Mrd_USD ~ CoVaR_Mrd_USD, result_05_reg)
summary(regression1)
```

```{r}
regression1 <- lm(SRISK_Mrd_USD ~  LRMES + Beta + Cor + Vol + Lvg, result_05_reg)
summary(regression1)
```

```{r}
regression1 <- lm(SRISK_Mrd_USD ~ CoVaR_Mrd_USD + LRMES + Beta + Cor + Vol + Lvg, result_05_reg)
summary(regression1)
```


```{r}
result_05_reg[order(result_05_reg$CoVaR_Mrd_USD),c(1,13)]
```



```{r,message=FALSE}
attach(result_05_reg)
names <- row.names(result_05_reg)

setwd("~/Dropbox/Research Seminar/R/Graphs/Ergebnisse")
png("Scatter_SRISK_CoVaR_05.png",width = 1400, height = 1000, res=110)

  
plot(CoVaR_Mrd_USD,SRISK_Mrd_USD,ylab="SRISK in Mrd.",xlab="CoVar in Mrd.",ylim=c(-45,0),xlim=c(-35,0))
text(CoVaR_Mrd_USD, SRISK_Mrd_USD,labels=names, cex=1 ,pos=4, offset = 0.7)
abline(lm(SRISK_Mrd_USD[CoVaR_Mrd_USD>-4] ~ CoVaR_Mrd_USD[CoVaR_Mrd_USD>-4]),lty=2)
abline(lm(SRISK_Mrd_USD ~ CoVaR_Mrd_USD),lty=1)
title("Scatterplot of SRISK and CoVaR")
legend(-8, -40, legend=c("Complete sample", "Without outliers (CoVar < -4"),
       , lty=1:2, cex=0.8)

dev.off()
```

```{r}
names(result_05_reg)
```

Is there a connection between VaR Diff and VaR sensibility?
===========================================================

A:
Yes there is a very clear connection. A linear regression and the scatterplot shows that institutions with a higher VaR Diff in % tend to have a higher VaR Sensibility.


```{r,message=FALSE}
i <- 5

attach(result_05_reg)
names <- row.names(result_05_reg[VaR_Diff<(-i),])




plot(VaR_Diff,Coefficient_05,ylab="VaR Sensibility",xlab="VaR Diff. in %") #,ylim=c(-45,0),xlim=c(-8,0))
text(VaR_Diff[VaR_Diff<(-i)],Coefficient_05[VaR_Diff<(-i)],labels=names, cex=0.75 ,pos=4, offset = 0.7)
#abline(lm(SRISK_Mrd_USD[CoVaR_Mrd_USD>-4] ~ CoVaR_Mrd_USD[CoVaR_Mrd_USD>-4]),lty=2)
abline(lm(Coefficient_05 ~ VaR_Diff),lty=1)
title("Scatterplot of SRISK and CoVaR")
legend(-8, -40, legend=c("Complete sample", "Without outliers (CoVar < -4"),
       , lty=1:2, cex=0.8)

reg1 <- summary(lm(Coefficient_05 ~ VaR_Diff))
plot(residuals(reg1))

summary(lm(SRISK_Mrd_USD ~ VaR_Diff_Mrd_USD))
```

```{r}
attach(result_05_reg)
i <- -2.5

names <- row.names(result_05_reg[VaR_Diff_Mrd_USD<(i),])

plot(CoVaR_Mrd_USD,SRISK_Mrd_USD,ylab="SRISK in Mrd.",xlab="VaR Diff. in Mrd.")
#text(VaR_Diff_Mrd_USD[VaR_Diff_Mrd_USD<(i)], SRISK_Mrd_USD[VaR_Diff_Mrd_USD<(i)],labels=names, cex=1 ,pos=4, offset = 0.7)
```


```{r}
attach(result_05_reg)
names <- row.names(result_05_reg)

plot(Coefficient_01,SRISK_Mrd_USD,ylab="SRISK in Mrd.",xlab="1% Qreg coefficient",ylim=c(-40,0))
text(Coefficient_01, SRISK_Mrd_USD,labels=names, cex=1 ,pos=4, offset = 0.7)
```

FRAGE:
Was erkl??rt den coefficient?
============================

The regression shows that the coefficient is at least partly correlated to the Beta and the leverage of the institutaions.
Additionally, it is also correlated to the 5% VaR quantile. ????

```{r}
regression1 <- lm(Coefficient_05  ~  VaR_quantil_05 + Beta + Lvg, result_05_reg)
summary(regression1)
```

FRAGE:
Which variables influence the 5% VaR quantile?
============================

Financial Institutions with a higher beta and a higher leverage tend to have higher 5% VaR quntiles. Both Coefficients are significant on the 1% level.

```{r}
regression1 <- lm(VaR_quantil_05  ~  Beta  + LRMES + Cor + Vol, result_05_reg)
summary(regression1)
```